---
title: "SOCIAL MEDIA AND WELLBEING"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill
runtime: shiny
---

```{r CSS for Colours}
# CSS is added below for the customisation of colours for flexdashboard headers and shinyWidgets button and slider colours. 
```

<style>                     
.navbar {
  background-color: #5CA3F3;
  border: none;
}

.btn-lightblue {
  color: #FFFFFF;
  background-color: #5CA3F3
}

.btn-lightblue.active {
  background-color: #1967be
}

.irs-bar {
    border-color: #FFFFFF;
    background-color: 5CA3F3;
}

.irs-from, .irs-to, .irs-single {
    color: #FFFFFF;
    background: #1967be;
}

.chart-title {
    color: #FFFFFF;
    background-color: #1967be;
}
</style>

```{r Setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
library(shinyWidgets)
library(ggpubr)   
library(shiny)
```

```{r Dataload}
PD_original <- read_csv(file = "proj_data.csv")
```

```{r context="setup"}

####Data cleanup#### 

final_data <- PD_original %>%                                    
  rename(
    Animals = Condition_Animals,
    Control = Condition_Control,
    Luxury = Condition_Luxury,
    Memes = Condition_Memes,
    Positive_Affect = PositiveAffect,
    Negative_Affect = NegativeAffect,
    Life_Satisfaction = LifeSatisfaction5
    ) %>%
  filter(!is.na(SWB)) %>% 
  select(-Finished, -Attrite) %>%
  mutate(
    Condition = factor(
      Condition, 
      levels = c(
        "Control",
        "Animals",
        "Luxury",
        "Memes")
      ))

####Data Preparation####

Reactive <- reactive({   
  FD2 <- final_data %>%          
         filter(
           Condition == "Control" |      
           Condition %in% input$cond,
           Time_Images > input$time[1],
           Time_Images < input$time[2]) 
  })

TT <- final_data %>% 
  filter(Time_Images >= 5)

####Boxplot functions####

pal <- c("#F8EE5C","#F9CA74","#FFA500","#FC8B03")

BoxPlot <- function(y_axis){
    ggplot(
      data = Reactive(), 
      mapping = aes_string(
        x = "Condition",
        y = y_axis,
        fill = "Condition"
        )) +
    geom_boxplot(
      na.rm = TRUE
      ) + 
    theme_minimal() + 
    scale_fill_manual(
      values = pal,
      guide = "none") +
    labs(
      x = NULL, 
      y = "Score") +
    theme(
      axis.text = element_text(face = "bold"), 
      axis.title = element_text(face = "bold")) +  
    ylim(1,5)
}

BoxPlot_inf <- function(y_axis){
    ggplot(
      data = TT, 
      mapping = aes_string(          
        x = "Condition",
        y = y_axis
        )) +
    geom_boxplot(
      fill = pal,
      na.rm = TRUE) + 
    theme_minimal() +
    labs(
      x = NULL, 
      y = "Score") +
    theme(
      axis.text = element_text(face = "bold"), 
      axis.title = element_text(face = "bold")) +
    stat_compare_means(
      label = "p.signif",
      method = "t.test",
      ref.group = "Control",
      label.y = 5.2,
      na.rm = TRUE) 
}
```        
         
Descriptive Statistics 
=====================================

Row {data-height=150}
-----------------------------------------------------------------------
```{r Button & Slider, context="render"}
checkboxGroupButtons(
   inputId = "cond",
   label = "Conditions",
   status = "lightblue",
   choices = c(
     "Luxury",
     "Animals",
     "Memes"),   
   selected = c(
     "Luxury",
     "Animals",
     "Memes"),
   individual = TRUE,
   width = "300px"
)

sliderInput(
  inputId = "time",                         
  label = "Time (secs)",
  min = 0, 
  max = 1600,
  value = c(0, 1600),
  ticks = FALSE,
  width = "400px"
  )
```

Row 
-----------------------------------------------------------------------

### **Positive Affect**
```{r, context="render"}
plotOutput("PA")
```

```{r, context="server"}
output$PA <- renderPlot({
  BoxPlot("Positive_Affect")
})
```


### **Negative Affect**
```{r, context="render"}
plotOutput("Neg")
```

```{r, context="server"}
output$Neg <- renderPlot({
  BoxPlot("Negative_Affect")
})
```


Row 
-----------------------------------------------------------------------

### **Life Satisfaction**
```{r, context="render"}
plotOutput("LS")
```

```{r, context="server"}
output$LS <- renderPlot({
  BoxPlot("Life_Satisfaction")
})
```


### **Subjective Well-Being**
```{r, context="render"}
plotOutput("SWB")
```

```{r, context="server"}
output$SWB <- renderPlot({
  BoxPlot("SWB")
})
```

Inferential Statistics
=====================================

Row 
-----------------------------------------------------------------------
### Positive Affect
```{r, context="render"}
plotOutput("PA_stat")
```

```{r, context="server"}

output$PA_stat <- renderPlot({
BoxPlot_inf("Positive_Affect")
})
```


### Negative Affect
```{r, context="render"}
plotOutput("NA_stat")
```

```{r, context="server"}
output$NA_stat <- renderPlot({
BoxPlot_inf("Negative_Affect")
})
```

Row 
-----------------------------------------------------------------------

### Life Satisfaction
```{r, context="render"}
plotOutput("LS_stat")
```

```{r, context="server"}
output$LS_stat <- renderPlot({
BoxPlot_inf("Life_Satisfaction")
})
```


### Subjective Well-Being
```{r, context="render"}
plotOutput("SWB_stat")
```

```{r, context="server"}
output$SWB_stat <- renderPlot({
BoxPlot_inf("SWB")
})
```

Row {data-height=20}
-----------------------------------------------------------------------
**NOTE:**

Row {data-height=20}
-----------------------------------------------------------------------
Comparisons were made between the Control condition and each of the social media conditions (Animals, Luxury, Memes). The significance of each comparison is labelled above the respective social media condition. 

Row {data-height=20}
-----------------------------------------------------------------------
**ns**   p > 0.05

Row {data-height=20}
-----------------------------------------------------------------------
**\*\***   p <= 0.01
